Generating Interactive WebSocket Applications in TypeScript

### 2020-03-03 PLACES_2020/encoding.tex
an HTML

\subparagraph{Send}
We make the assumption that message sending is triggered by
some user-driven UI event (e.g. clicking a button, pressing a key on the
keyboard) which interacts with some DOM element.
We could pass a
\texttt{send()} function as a prop to the sending state, but the developer
would be free to call the function multiple times which makes channel reuse
possible.
Instead, we pass a \textit{factory function} as a prop, which will,
given a HTML event and an event handler function, return a fresh React
component that binds the sending action on construction.
So once the bound event is triggered, our session runtime executes the event
handler function to obtain the payload to send, perform the send
\textit{exactly once} and transition to (which, in practice, means render) the
successor state.

@@

We demonstrate the semantics using the \textit{Noughts and Crosses} example in
\cref{lst:clientapp}.
\texttt{this.props.Pos} is the factory function prop
passed from the session runtime.
For each x-y coordinate on the game board, we
create a \texttt{SelectPoint} React component from the factory function (which
reads ``build a React component that sends the \texttt{Pos} message with x-y
coordinates as payload when the user clicks on it'') and we wrap a table cell
(the game board is rendered as a HTML table) inside the \texttt{SelectPoint}
component to bind the click event on the table cell.

>>>>

\subparagraph{Send}
We make the assumption that message sending is triggered by
some user-driven UI event (e.g. clicking a button, pressing a key on the
keyboard) which interacts with some DOM element.
We could pass a
\texttt{send()} function as a prop to the sending state, but the developer
would be free to call the function multiple times which makes channel reuse
possible.
Instead, we pass a \textit{factory function} as a prop, which will,
given an HTML event and an event handler function, return a fresh React
component that binds the sending action on construction.
So once the bound event is triggered, our session runtime executes the event
handler function to obtain the payload to send, perform the send
\textit{exactly once} and transition to (which, in practice, means render) the
successor state.

@@

We demonstrate the semantics using the \textit{Noughts and Crosses} example in
\cref{lst:clientapp}.
\texttt{this.props.Pos} is the factory function prop
passed from the session runtime.
For each x-y coordinate on the game board, we
create a \texttt{SelectPoint} React component from the factory function (which
reads ``build a React component that sends the \texttt{Pos} message with x-y
coordinates as payload when the user clicks on it'') and we wrap a table cell
(the game board is rendered as an HTML table) inside the \texttt{SelectPoint}
component to bind the click event on the table cell.
